QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-3.tex
fix double "and" and other minor fixes

At the end of this process we had gathered more than eight thousand
instances. Three quarters of them contained discrete variables, while
the remainder contained only continuous variables. In more detail,
we gathered $\approx 1800$ Quadratic Binary Linear (QBL) instances,
$\approx 2000$ Quadratic Continuous Quadratic (QCQ) instances, and
and $\approx 2500$ Quadratic General Quadratic (QGQ) instances. We
also received $\approx 1000$ Convex General Convex (CGC) instances. We
obtained relatively fewer Quadratic Binary Quadratic (QBQ), Convex
Continuous Convex (CCC) and Convex Mixed Convex (CMC) instances,
($\approx 150$, $\approx 200$ and $\approx 200$ instances respectively).
Finally, we found only $17$ Quadratic Mixed
Linear (QML) instances. In the call for instances, no specific formats
requirements were imposed for the submissions.

>>>>

At the end of this process we had gathered more than eight thousand
instances. Three quarters of them contained discrete variables, while
the remainder contained only continuous variables. In more detail,
we gathered $\approx 1800$ Quadratic Binary Linear (QBL) instances,
$\approx 2000$ Quadratic Continuous Quadratic (QCQ) instances,
and $\approx 2500$ Quadratic General Quadratic (QGQ) instances. We
also received $\approx 1000$ Convex General Convex (CGC) instances. We
obtained relatively fewer Quadratic Binary Quadratic (QBQ), Convex
Continuous Convex (CCC) and Convex Mixed Convex (CMC) instances,
($\approx 150$, $\approx 200$, and $\approx 200$ instances, respectively).
Finally, we found only $17$ Quadratic Mixed
Linear (QML) instances. In the call for instances, no specific format
requirements were imposed for the submissions.
